---
title: "Probability distributions plots for visual identification (for different parameters)"
author: "Mr.Pardeshi"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


## Including Plots

## Exponential distribution (scale parameter) plots for different scale parameters:
```{r}
# this is our interest
n2=50
list_r2=list()
y=c()
library(tibble)
k=c(1,13,50)
J=c(0.1,1,2,3)  # rates 

for( j in 1:length(J)){
   r=rexp(500,rate=J[j])
   list_r2[[j]]=r
}
color=c("blue","black","gold","orange")
plot(density(list_r2[[1]]),lwd=2,col="blue",main="Density plot of exp for same r.n size but diff rates" )
for (i in 2:4){
lines(density(list_r2[[i]]),lwd=2,col=color[i])
legend("topright",legend=paste("rate=",J),fill=c("blue","black","gold","orange"))
}
```


## Exponential distribution (location parameter) plots for different location parameters:

```{r}
n2=500
list_r3=list()
y=c()
library(tibble)
k=c(1,13,50)
J1=c(0,1,2,3)

for( j in 1:length(J1)){
   r=rexp(500,rate=0.5) + J1[j]
   list_r3[[j]]=r
}
color=c("blue","black","gold","orange")
plot(density(list_r3[[1]]),lwd=2,col="blue",main="Density plot of exp for same rates but diff locations" )
for (i in 2:4){
lines(density(list_r3[[i]]),lwd=2,col=color[i])
legend("topright",legend=paste("location=",J1),fill=c("blue","black","gold","orange"))
}
```

```{r}
# for cauchy distribution (scale parameter)
n=50
list_r3=list()
y=c()
J=c(0.09,0.25,0.73,1)

  for( j in 1:length(J)){
   r=(rcauchy(n,0,J[j]))  # scale parameter is > 0 always
   list_r3[[j]]=r
  }
D4=data.frame('s1'=(list_r3[[1]]),'s2'=(list_r3[[2]]),'s3'=(list_r3[[3]]),'s4'=(list_r3[[4]]))
library(ggplot2)
library(tidyverse)
D4_long=D4 |> pivot_longer(cols=everything (),names_to='Series',values_to='Values')

fig2=ggplot(D4)+
geom_density(aes(s1),fill='blue',lwd=1)+
  geom_density(aes(s2),fill='skyblue',lwd=1)+
  geom_density(aes(s3),fill='navy',lwd=1)+
  geom_density(aes(s4),fill='orange',lwd=1)+
  labs(title='Density plot of cauchy distribution with respect to different location parameter',
       x='Values',
       y='Density',
       color='Series')+
  coord_cartesian(xlim=c(-10,10))
  theme_minimal()
library(plotly)
ggplotly(fig2)



```

## Cauchy for location parameter
```{r}
# for cauchy distribution (location parameter)
n=50
list_r4=list()
J=c(0,1,2,5)

  for( j in 1:length(J)){
   r=(rcauchy(n,J[j],1))  # location parameter is > 0 always
   list_r4[[j]]=r
  }
D=data.frame('s1'=(list_r4[[1]]),'s2'=(list_r4[[2]]),'s3'=(list_r4[[3]]),'s4'=(list_r4[[4]]))
library(ggplot2)
library(tidyverse)
D_long=D |> pivot_longer(cols=everything (),names_to='Series',values_to='Values')

fig3=ggplot(D)+
geom_density(aes(s1),fill='darkred',lwd=1)+
  geom_density(aes(s2),fill='skyblue',lwd=1)+
  geom_density(aes(s3),fill='navy',lwd=1)+
  geom_density(aes(s4),fill='orange',lwd=1)+
  labs(title='Density plot of cauchy distribution with respect to different location parameter',
       x='Values',
       y='Density',
       color='Series')+
  coord_cartesian(xlim=c(-30,30))
  theme_minimal()
library(plotly)
ggplotly(fig3)


```

## Cauchy distribution plots for different locations andd scale parameter
```{r}
# for cauchy distribution (location and scale parameter)
n=50
list_r4=list()
J=c(0,1,2,5)
S=c(0.09,0.25,0.73,1)
for (i in 1:length(S)){
  for( j in 1:length(J)){
   r=(rcauchy(n,J[j],S[i[]]))  # location parameter is > 0 always
   list_r4[[j]]=r
}}
color=c("blue","black","gold","orange")
plot(density(list_r4[[1]]),lwd=3,col="blue",main="Density plot of cauchy at diff scales and locations" ,xlim=c(-60,60))
for (i in 2:4){
lines(density(list_r4[[i]]),lwd=3,col=color[i])
legend("topright",legend=paste("location=",J),fill=c("blue","black","gold","orange"))
}

```

## Gamma distribution plots for different shapes but constant rates
```{r}
n=100
list_r5=list()
y=c()
S=c(0.1,1,2,3)

  for( j in 1:length(J)){
   r=(rgamma(n,S[j],1))  # shape parameter >0  rate parameter =1 , scale =1/rate
   list_r5[[j]]=r
  }
D2=data.frame('s1'=(list_r5[[1]]),'s2'=(list_r5[[2]]),'s3'=(list_r5[[3]]),'s4'=(list_r5[[4]]))
library(ggplot2)
library(tidyverse)
D2_long=D2 |> pivot_longer(cols=everything (),names_to='Series',values_to='Values')

fig_1=ggplot(D2)+
geom_density(aes(s1),fill='darkblue',lwd=1)+
  geom_density(aes(s2),fill='blue',lwd=1)+
  geom_density(aes(s3),fill='skyblue',lwd=1)+
  geom_density(aes(s4),fill='orange',lwd=1)+
  labs(title='Density plot of gamma distribution with respect to different shape but constant rate parameter',
       x='Values',
       y='Density',
       color='Series')+
  coord_cartesian(xlim=c(0,2),ylim=c(0,3))
  theme_minimal()
library(plotly)
ggplotly(fig_1)



```

## Gamma distribution for different rates but constant shape
```{r}
n=100
list_r6=list()
y=c()
S=c(0.09,0.25,0.73,0.99)

  for( j in 1:length(J)){
   r=(rgamma(n,1,R[j]))  # shape parameter >0  rate parameter =1 , scale =1/rate
   list_r6[[j]]=r
}
color=c("blue","darkblue","gold",'green')
plot(density(list_r[[1]]),lwd=3,col="blue",main="Density plot of gamma dist at diff shape & rate",xlim=c(-10,10) )
for (i in 2:3){
lines(density(list_r6[[i]]),lwd=3,col=color[i])
legend("topright",legend=paste("Shape=",S),fill=c("blue","darkblue","gold",'green'))
}
```


```{r}
# for gamma distribution for different shape and rates

n=100
list_r5=list()
y=c()
R=c(0.5,1,2,3)
S=c(0,1,2,3)

  for( j in 1:length(J)){
   r=(rgamma(n,S[j],J[j]))  # shape parameter >0 & rate parameter >0
   list_r5[[j]]=r
  }

D3=data.frame('s1'=(list_r5[[1]]),'s2'=(list_r5[[2]]),'s3'=(list_r5[[3]]),'s4'=(list_r5[[4]]))
library(ggplot2)
library(tidyverse)
D3_long=D3 |> pivot_longer(cols=everything (),names_to='Series',values_to='Values')

ggplot(D3)+
geom_density(aes(s1),fill='darkred',lwd=1)+
  geom_density(aes(s2),fill='skyblue',lwd=1)+
  geom_density(aes(s3),fill='navy',lwd=1)+
  geom_density(aes(s4),fill='orange',lwd=1)+
  labs(title='Density plot of gamma distribution with respect to different rate and shape parameter',
       x='Values',
       y='Density',
       color='Series')+
  coord_cartesian(xlim=c(-2,6))
  theme_minimal()


```

```{r}
# for beta distributions

n=100
list_r=list()
y=c()
S1=c(0,2,1)
S2=c(0,1,2)

  for( j in 1:length(S1)){
   r=(rgamma(n,S1[j],S2[j]))  # shape1 parameter >0 for success & shape2 parameter >0 for failure
   list_r[[j]]=r
}
color=c("blue","black","gold")
plot(density(list_r[[1]]),lwd=2,col="blue",main="Density plot of beta dist at diff shape1 & shape2" )
for (i in 2:3){
lines(density(list_r[[i]]),lwd=2,col=color[i])
legend("topright",legend=c(paste("shape1=",S1),paste("Shape2=",S2)),fill=c("blue","black","gold"))
}

```

```{r}
# Plots of  Poisson distribution for different lambda's
n=50
list_r=list()
lambda=c(0.1,1.5,2.19,5)
  for( j in 1:length(lambda)){
   r=(rpois(n,lambda[j]))  # shape1 parameter >0 for success & shape2 parameter >0 for failure
   list_r[[j]]=r
  }
D1=data.frame('s1'=(list_r[[1]]),'s2'=(list_r[[2]]),'s3'=(list_r[[3]]),'s4'=(list_r[[4]]))
library(ggplot2)
library(tidyverse)
D1_long=D1 |> pivot_longer(cols=everything (),names_to='Series',values_to='Values')

fig4=ggplot(D1)+
geom_density(aes(s1),fill='darkgreen',lwd=1)+
  geom_density(aes(s2),fill='green',lwd=1)+
  geom_density(aes(s3),fill='lightgreen',lwd=1)+
  geom_density(aes(s4),fill='green4',lwd=1)+
  labs(title='Density plot of poisson distribution with respect to different parameter',
       x='Values',
       y='Density',
       color='Series')+
  theme_minimal()
library(plotly)
ggplotly(fig4)



```

## Plot for binomial distribution
```{r}

# Plots of  Poisson distribution for different lambda's
n=50
list_r6=list()
p=c(0.12,0.25,0.56,0.89)
  for( j in 1:length(lambda)){
   r=(rbinom(n,1000,p[j]))  # shape1 parameter >0 for success & shape2 parameter >0 for failure
   list_r6[[j]]=r
  }
D1=data.frame('s1'=(list_r6[[1]]),'s2'=(list_r6[[2]]),'s3'=(list_r6[[3]]),'s4'=(list_r6[[4]]))
library(plotly)
library(tidyverse)
D1_long=D1 |> pivot_longer(cols=everything (),names_to='Series',values_to='Values')
fig = plot_ly()
fig = fig |>
    add_trace(x=D1$s1,type='histogram',histnorm='probability density',name='s1',opacity=0.6) |>
  add_trace(x=D1$s2,type='histogram',histnorm='probability density',name='s2',opacity=0.6) |>
  add_trace(x=D1$s3,type='histogram',histnorm='probability density',name='s3',opacity=0.6) |>
  add_trace(x=D1$s4,type='histogram',histnorm='probability density',name='s4',opacity=0.6) 
fig
   
   
   


```


